---
title: "Ejercicios de repaso"
author: "JFMRA"
date: "22 de enero de 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Punto 1 pag 152

```{r}

ballthrows <- function(prob){
  res <- rbinom(1, size = 1, prob = prob)
  
  while(TRUE){
    temp <- rbinom(1, size = 1, prob = prob)
    res <- c(res, temp)
    
    cond <- sum(res[c(length(res)-1, length(res))])
    if (cond == 0){break}
  }
  res
}

attempt <- ballthrows(0.6)

attempt



```

```{r}
simulation <- lapply(rep(0.6, 10000),ballthrows)

points <- lapply(simulation, sum)
n_attempts <- lapply(simulation, length)

plot(n_attempts, points)

W <- table(unlist(n_attempts))

barplot(W)
mean(W)
sd(W)

```


## Preguntas adicionales 
### a. calcule 

```{r}
simulation <- lapply(rep(0.6, 10000),ballthrows)

W <- unlist(lapply(simulation, length))
W
```

```{r}
ballthrows <- function(prob){
  res <- rbinom(1, size = 1, prob = prob)
  
  while(TRUE){
    temp <- rbinom(1, size = 1, prob = prob)
    res <- c(res, temp)
    
    cond <- sum(res[c(length(res)-1, length(res))])
    if (cond == 0){break}
  }
  return(length(cond))
}

W2 <- replicate(n = 10000, ballthrows)
```





2) Continuous probability simulation: the logarithms of weights (in pounds) of men
in the United States are approximately normally distributed with mean 5.13
and standard deviation 0.17; women with mean 4.96 and standard deviation
0.20. Suppose 10 adults selected at random step on an elevator with a capacity
of 1750 pounds. What is the probability that the elevator cable breaks?

```{r}
meanhom <- 5.13; meanmuj <- 4.96
sdhom <- 0.17; sdmuj <- 0.2

select <- function(n = 10){
  sexos <- sample(0:1, n, replace = T) #Hombres = 1, mujeres = 2
  pesos <- exp(
    c(rnorm(sum(sexos), meanhom, sdhom), 
      rnorm(n-sum(sexos), meanmuj, sdmuj)))
  return(sum(pesos))
}

res <- replicate(10000,select())

res_resumen <- table(res > 1750)
barplot(res_resumen, names.arg(c("No se quiebra", "Se quiebra")))
```


